General constraints on magic state protocols from the statistical mechanics of \\Wigner negativity

### 2021-06-25 magic_paper.tex
minor changes

The coordinates of the first point after the origin for $\rho_S(\epsilon)^{\otimes n}$ are given by $(1/9^n, v(\epsilon)^n)$, while for $\rho_S(\epsilon')^{\otimes n'}$ by $(1/9^{n'}, v(\epsilon')^{n'})$, and by considering the slope of the line segment joining this point to the origin we can use~\cref{prop:first_elb} in the Appendices, to bound $R(\epsilon, \epsilon')$. We find that
\begin{equation}\label{eq:unital-bound}
	R(\epsilon, \epsilon') \leq R_\infty :=\frac{\ln (3-4\epsilon)}{\ln (3-4\epsilon')}.
\end{equation}
The choice of denoting the bound by $R_\infty$ is explained in Section \ref{section:entropies} in relation to single-shot entropies. For the limiting case of pure magic states on the output ($\epsilon'=0$), this simplifies to
\begin{equation}
	R \leq 1 + \frac{\ln (1 - \frac{4}{3} \epsilon)}{\ln 3}.
\end{equation}
We compare this to other known distillation bounds coming from mana and thauma~\cite{Wang_2020}. The mana bound can be directly calculated as
\begin{equation}
	R \leq \frac{\M(\rho_{\rm{S}}(\epsilon))}{\M(\rho_{\rm{S}}(0))} = 1 + \frac{\ln \left(1 - \frac{8}{15}\epsilon \right)}{\ln \frac{5}{3}}.
\end{equation}
The recently introduced max--thauma~\cite{Wang_2020} is defined as
\begin{equation}
	\theta_{\rm{max}}(\rho) \coloneqq \log{\min{\{2\hspace{1pt}\sn{V}+1 : V \geq \rho\}}}
\end{equation}
and can be calculated numerically via a semi-definite program. For the noisy Strange state, the max--thauma bound coincides with the mana bound, and we find that they are both looser than the majorization bound $R_\infty$ as shown in~\cref{fig:distill_bounds}.

@@

Our bound depends on the von Neumann entropy $S(\rho)$ of a state, and the free energy at a particular temperature.
For a state $\tau = e^{-\beta H}/\Z$, the Helmholtz free energy $F$ is given by
\begin{equation}
	F \coloneqq \tr[H \tau] - \beta^{-1}S(\tau) = -\beta^{-1}\log{\Z},
\end{equation}
which is obtained from the internal energy via a Legendre transform~\cite{Pathria_1997}.

@@

\begin{proposition}
    \label{thm:wchannel}
    The Wigner distribution of a quantum channel $\E: \cal{B}(\cal{H}_{d_A}) \rightarrow \cal{B}(\cal{H}_{d_B})$ is
    \begin{enumerate}
        \item[(i)]\label{en:wo1} Real-valued: $\W{\E}(\z|\y) \in \mathbb{R}^{d_A^2} \times \mathbb{R}^{d_B^2}$;
        \item[(ii)]\label{en:wo2} Normalised: $\sum_{\bmy \in \cal{P}_{d_B}} \W[\bmz|\bmy]{\E} = 1$ \\ 
        for any $\bmz \in \cal{P}_{d_A}$;
        \item[(iii)]\label{en:wo3} Bounded: $\abs{\W[\bmy|\bmz]{\E}} \leq \frac{d_A}{d_B}$;
	    \item[(iv)]\label{en:wo4} $\W[\bmy]{\E(\rho)} = \sum\limits_{\bmz \in \cal{P}_{d_{A}}} \W[\bmy|\bmz]{\E} \W[\bmz]{\rho}$ for any $\bmy \in \cal{P}_{d_B}$.
    \end{enumerate}
\end{proposition}
\begin{proof}
	Proof of all properties are provided in~\cite{Wang_2019} except for property (iii) which is a direct consequence of the definition of $\W{\E}$ and property (iii) in~\cref{thm:wstate}.
\end{proof}

@@

Conversely, suppose a bistochastic map $B$ exists sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$. Again, define $A: \mathbb{R}^N \mapsto \mathbb{R}^{N'}$ by $A := \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma}$ so that it is stochastic as a composition of stochastic maps and $A \w = \big( \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma} \big) \w = \w'$, as well as $A \r = \r'$.
\end{proof}
We note that the vectors $\r, \r'$ with rational components form a dense subset of the positive probability distributions, do not consider technical fine-print that would not affect actual physical measurements, which always have a finite resolution.
\subsection{Component-multiplicity pairs}
\label{app:cmpairs}

>>>>

The coordinates of the first point after the origin for $\rho_S(\epsilon)^{\otimes n}$ are given by $(1/9^n, v(\epsilon)^n)$, while for $\rho_S(\epsilon')^{\otimes n'}$ by $(1/9^{n'}, v(\epsilon')^{n'})$, and by considering the slope of the line segment joining this point to the origin we can use~\cref{prop:first_elb} in the Appendices, to bound $R(\epsilon, \epsilon')$. We find that
\begin{equation}\label{eq:unital-bound}
	R(\epsilon, \epsilon') \leq R_\infty :=\frac{\ln (3-4\epsilon)}{\ln (3-4\epsilon')}.
\end{equation}
The choice of denoting the bound by $R_\infty$ is explained in Section \ref{section:entropies} in relation to single-shot entropies. For the limiting case of pure magic states on the output ($\epsilon'=0$), this simplifies to
\begin{equation}
	R \leq 1 + \frac{\ln (1 - \frac{4}{3} \epsilon)}{\ln 3}.
\end{equation}
We compare this to other known distillation bounds coming from mana and thauma~\cite{Wang_2020}. The mana bound can be directly calculated as
\begin{equation}
	R \leq \frac{\M(\rho_{\rm{S}}(\epsilon))}{\M(\rho_{\rm{S}}(0))} = 1 + \frac{\ln \left(1 - \frac{8}{15}\epsilon \right)}{\ln \frac{5}{3}}.
\end{equation}
The recently introduced max--thauma~\cite{Wang_2020} is defined as
\begin{equation}
	\theta_{\rm{max}}(\rho) \coloneqq \log \min{\{2\hspace{1pt}\sn{V}+1 : V \geq \rho\}}
\end{equation}
and can be calculated numerically via a semi-definite program. For the noisy Strange state, the max--thauma bound coincides with the mana bound, and we find that they are both looser than the majorization bound $R_\infty$ as shown in~\cref{fig:distill_bounds}.

@@

Our bound depends on the von Neumann entropy $S(\rho)$ of a state, and the free energy at a particular temperature.
For a state $\tau = e^{-\beta H}/\Z$, the Helmholtz free energy $F$ is given by
\begin{equation}
	F \coloneqq \tr[H \tau] - \beta^{-1}S(\tau) = -\beta^{-1}\log \Z,
\end{equation}
which is obtained from the internal energy via a Legendre transform~\cite{Pathria_1997}.

@@

\begin{proposition}
    \label{thm:wchannel}
    The Wigner distribution of a quantum channel $\E: \cal{B}(\cal{H}_{d_A}) \rightarrow \cal{B}(\cal{H}_{d_B})$ is
    \begin{enumerate}
        \item[(i)]\label{en:wo1} Real-valued: $\W{\E}(\bmz|\bmy) \in \mathbb{R}^{d_A^2} \times \mathbb{R}^{d_B^2}$;
        \item[(ii)]\label{en:wo2} Normalised: $\sum_{\bmy \in \cal{P}_{d_B}} \W[\bmz|\bmy]{\E} = 1$ \\ 
        for any $\bmz \in \cal{P}_{d_A}$;
        \item[(iii)]\label{en:wo3} Bounded: $\abs{\W[\bmz|\bmy]{\E}} \leq \frac{d_A}{d_B}$;
	    \item[(iv)]\label{en:wo4} $\W[\bmz]{\E(\rho)} = \sum\limits_{\bmy \in \cal{P}_{d_{A}}} \W[\bmz|\bmy]{\E} \W[\bmy]{\rho}$ for any $\bmz \in \cal{P}_{d_B}$.
    \end{enumerate}
\end{proposition}
\begin{proof}
	Proof of all properties are provided in~\cite{Wang_2019} except for property (iii) which is a direct consequence of the definition of $\W{\E}$ and property (iii) in~\cref{thm:wstate}.
\end{proof}

@@

Conversely, suppose a bistochastic map $B$ exists sending $\Gamma_{\bma}(\w)$ to $\Gamma_{\bma'}(\w')$. Again, define $A: \mathbb{R}^N \mapsto \mathbb{R}^{N'}$ by $A := \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma}$ so that it is stochastic as a composition of stochastic maps and $A \w = \big( \Gamma_{\bma'}^{-1} \circ B \circ \Gamma_{\bma} \big) \w = \w'$, as well as $A \r = \r'$.
\end{proof}
We note that the vectors $\r, \r'$ with rational components form a dense subset of the positive probability distributions, and do not consider further technicalities that have no impact on actual physical measurements, which always have a finite resolution.
\subsection{Component-multiplicity pairs}
\label{app:cmpairs}
